Turnover of species and interactions

### 2018-10-26 paper/data-exploration/turnover.Rmd
Log x axis

sp_deg_rank %>%
  ggplot(aes(x = deg, y = n_loc)) +
  geom_point(aes(colour = selected, fill = selected, shape = guild)) +
  geom_label_repel(data = dplyr::filter(sp_deg_rank, selected), 
                  aes(label = sp_name), size = 3, fontface =  "italic",
                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
  # scale_x_log10() +
  scale_y_log10() +
  scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(21, 24)) +
  guides(color = guide_legend("focal species"), 
         fill = guide_legend("focal species")) +
  theme_bw() +
  theme(legend.position = c(0.02,0.98), 
        legend.justification = c(0,1), 
        legend.box = "horizontal") +
  labs(title = "species degree vs. number of locations", 
       subtitle = "there are 16 focal species, mostly generalist pollinators",
       caption = "focal species are those that have the same interaction in >= 3 locations and are present >= 5 locations", 
       y = "# locations", 
       x = "species degree")

>>>>

sp_deg_rank %>%
  ggplot(aes(x = deg, y = n_loc)) +
  geom_point(aes(colour = selected, fill = selected, shape = guild)) +
  geom_label_repel(data = dplyr::filter(sp_deg_rank, selected), 
                  aes(label = sp_name), size = 3, fontface =  "italic",
                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
  scale_x_log10() +
  # scale_y_log10() +
  scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(21, 24)) +
  guides(color = guide_legend("focal species"), 
         fill = guide_legend("focal species")) +
  theme_bw() +
  theme(legend.position = c(0.02,0.98), 
        legend.justification = c(0,1), 
        legend.box = "horizontal") +
  labs(title = "species degree vs. number of locations", 
       subtitle = "there are 16 focal species, mostly generalist pollinators",
       caption = "focal species are those that have the same interaction in >= 3 locations and are present >= 5 locations", 
       y = "# locations", 
       x = "species degree")
